Effects of Fishing on Scarid Grazing Behavior in the Caribbean

### 2018-01-31 DonorReport.Rmd
updates 1/31

---
title: "Effects of Fishing on Scarid Grazing Behavior in the Caribbean"
author: "Molly Wilson"
date: "1/5/2018"
output:
  pdf_document:
    toc: yes
  html_document:
    number_sections: yes
    theme: united
    toc: yes
    toc_float: yes
    toc_depth: 3
---

@@

```{r, eval=FALSE}
Thanks to generous funding awarded through the UCSB Research Accellerator Award, I was able to travel to Antigua along with a research assistant also working on her Ph.D. in marine ecoogy and fisheries management. The funds supplied us with SCUBA tanks, survey gear, boat fuel, a car rental to transport gear, and fuel and food to supply a four-day boat trip to Barbuda. During the three weeks we were in the field, we collected benthic and fish survey data at a total of nine sites which, in addition to providing data for this investigation, will also serve as valuable assessment and baseline data for future studies. Across the nine sites we coolected behavioral data from a total of 434 individual parrotfish, making a database of nearly 800 fish follows when integrated with the data I collected in Bonaire. While the data analysis is still ongoing, the preliminary results are extremely interesting. This research would not have been possible without the generous support of my Research Accellerator sponsor.
```

>>>>

---
title: "Effects of Fishing on Scarid Grazing Behavior in the Caribbean"
author: "Molly Wilson"
date: "1/5/2018"
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
    toc_float: yes
    toc_depth: 3
  pdf_document:
    toc: yes
---

@@

Thanks to generous funding awarded through the UCSB Research Accellerator Award, I was able to travel to Antigua along with a research assistant also working on her Ph.D. in marine ecoogy and fisheries management. The funds supplied us with SCUBA tanks, survey gear, boat fuel, a car rental to transport gear, and fuel and food to supply a four-day boat trip to Barbuda. During the three weeks we were in the field, we collected benthic and fish survey data at a total of nine sites which, in addition to providing data for this investigation, will also serve as valuable assessment and baseline data for future studies. Across the nine sites we coolected behavioral data from a total of 434 individual parrotfish, making a database of nearly 800 fish follows when integrated with the data I collected in Bonaire. While the data analysis is still ongoing, the preliminary results are extremely interesting. This research would not have been possible without the generous support of my Research Accellerator sponsor.
